DRAFT Example Kitsap County Pedestrian Facilities Metrics/Evaluation Report

### 2022-10-01 Draft Ped Metrics Example.Rmd
add palette for sidewalks and shoulders data

>>>>

# NOTE: Also make this a factor so that it is sorted properly!!
sw_sh_col <- scale_color_manual(values = c("Sidewalk: 3 ft"="#E41A1C",
                                           "Sidewalk: 4 ft"="#874F6F",
                                           "Sidewalk: 5 ft"="#3881B0",
                                           "Sidewalk: 8 ft"="#449B75",
                                           "Paved Shoulder: 1 ft"="#56A255",
                                           "Paved Shoulder: 2 ft"="#7E6E85",
                                           "Paved Shoulder: 3 ft"="#AC5782",
                                           "Paved Shoulder: 4 ft"="#E3712B", 
                                           "Paved Shoulder: 5 ft"="#FFA10D",
                                           "Paved Shoulder: 6 ft"="#FFE528",
                                           "Paved Shoulder: 7 ft"="#E1C62F",
                                           "Paved Shoulder: 8 ft"="#B16C29",
                                           "Paved Shoulder: 10 ft"="#C66764",
                                           "Paved Shoulder: 12 ft"="#F17EB4",
                                           "Paved Shoulder: 15 ft"="#CB8CAD",
                                           "Paved Shoulder: 17 ft"="#999999"))
nc_sw_sh$TYPE <- factor(nc_sw_sh$TYPE, levels = c("Sidewalk: 3 ft",
                                                  "Sidewalk: 4 ft",
                                                  "Sidewalk: 5 ft",
                                                  "Sidewalk: 8 ft" ,
                                                  "Paved Shoulder: 1 ft",
                                                  "Paved Shoulder: 2 ft",
                                                  "Paved Shoulder: 3 ft",
                                                  "Paved Shoulder: 4 ft", 
                                                  "Paved Shoulder: 5 ft",
                                                  "Paved Shoulder: 6 ft",
                                                  "Paved Shoulder: 7 ft",
                                                  "Paved Shoulder: 8 ft",
                                                  "Paved Shoulder: 10 ft",
                                                  "Paved Shoulder: 12 ft",
                                                  "Paved Shoulder: 15 ft",
                                                  "Paved Shoulder: 17 ft"))
```
